Online {\IterComp}

### 2017-11-16 related.tex
related work. added two of grigori's papers

Fursin~\etal~\cite{fursin07} attempted to find a general approach for online \itercomp. They proposed to use instructions per cycle (IPC)
as a metric for comparing different runs of the same program with different optimization settings and different inputs. Their hypothesis is
that application binaries displaying higher IPC are more efficient than lower IPC binaries. However, many optimization techniques affect
IPC in the opposite way, making the program more efficient while lowering IPC. The authors in~\cite{fursin07} acknowledge that this limits
the applicability of IPC for \itercomp. In the context of multithreaded applications, IPC cannot be used to compare the performance of
different runs even when they use the same intput~\cite{alameldeen06,eyerman08}. Work-related metrics are shown to be more appropriate, but prior work
relied on application-specific work metrics. This paper presents the first automatic and application agnostic approach for deriving a work metric.

>>>>

Older works attempted to drive \itercomp with execution time information~\cite{fursin:hal-01257279,fursin:inria-00001054}. They create
multiple versions of the hottest procedures, optimized and unoptimized, and at runtime randomly and dynamically select which one to use.
For each invocation, they record the time spent in the procedure and the version used. By comparing the average time required for each
invocation, they are able to evaluate the relative performance of different optimizations. The limitations of this approach are that it
depends on the amount of work performed by the procedure not changing dramatically from invocation to invocation and the number of
invocations being sufficiently high to collect multiple data points for each version. These drawbacks keep it from being a general solution
to the problem of iterative compilation.

Fursin~\etal~\cite{fursin07} attempted to find such a general approach. They proposed to use instructions per cycle (IPC)
as a metric for comparing different runs of the same program with different optimization settings and different inputs. Their hypothesis is
that application binaries displaying higher IPC are more efficient than lower IPC binaries. However, many optimization techniques affect
IPC in the opposite way, making the program more efficient while lowering IPC. The authors in~\cite{fursin07} acknowledge that this limits
the applicability of IPC for \itercomp. Our experiments in Section~\ref{sec:motivation} also show that IPC is not an appropriate metric
for quantifying efficiency for iterative compilation. In the context of multithreaded applications, IPC cannot be used to compare the performance of
different runs even when they use the same intput~\cite{alameldeen06,eyerman08}. Work-related metrics are shown to be more appropriate, but prior work
relied on application-specific work metrics. This paper presents the first automatic and application agnostic approach for deriving a work metric.
